---
title: "Rproject_template_rmarkdown"
author: "DKL"
date: "2023-07-01"
output:
  html_document:
    fig_caption: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
#If you don't want to show the code
#knitr::opts_chunk$set(echo = FALSE, message = FALSE)
 
```

```{r}
library(tidyverse)
#conflict_prefer("filter", "dplyr")
library(broom)
library(knitr)
```

## Report
In this report we evaluate the relationship between petal length and sepal width for irises.

```{r iris}
data(iris)
iris_nonsetosa <- iris %>%
  filter(Species != "setosa")
```

The original data set has `r iris$Species %>% unique() %>% length()` species, 
but we will only work with `r iris_nonsetosa$Species %>% unique() %>% length()`
of them. 

### Model

The model results are below.

```{r caption = "Table 1"}
m_pl_sw <- lm(Petal.Length ~ Sepal.Width, data = iris_nonsetosa)
tidy_m_pl_sw <- tidy(m_pl_sw)
kable(tidy_m_pl_sw,
      caption="Table 1. Regression output for predictiong petal length for sepal width.",
      digits = 2)
```

The slope of the regression model is `r tidy_m_pl_sw %>% filter(term == "Sepal.Width") %>% pull(estimate) %>% round(2)`.

## Visualize

The figure below shows the relationship between these variables, and we observe a positive slope in this visualization as well. 

```{r fig.cap = "Figure 2. Relationship between petal length and sepal width"}
ggplot(iris_nonsetosa) +
  geom_point(aes(x = Sepal.Width, y = Petal.Length, color = Species)) +
  geom_smooth(aes(x= Sepal.Width, y= Petal.Length), method = "lm")
```
# Set echo = FALSE if your audience do not have to see the code. 